### 2017-05-30 paper.tex
Add DOI providers, tweak wording

The traditional academic system has limited ways of recognizing contributions.
Until systems have been expanded to improve this,
it is important to publish your lessons using a mechanism that provides recognition to the contributors.
Currently an effective way to do this is
to publish lessons with a DOI supplied by (FIXME list possibilities).
Contributors can be listed as authors
and the maintainers of the lesson as editors
to provide differentiated recognition of their contributions.

A lesson release is a good opportunity to bring the material into a stable shape
by fixing outstanding issues and merging contribution.
The complete name and possible identifier like ORCID should also be gathered for every contributor.
Version control helps a lot in continuously maintaining a list of contributors
but also in remembering which version is used for release
(e.g., using branches or tags).
A lesson release is here to stay
and it is recommended to use a consistent naming scheme from the beginning.
A convenient naming scheme is to use the full year and month of the release,
like ``2017.05'',
as it conveys a clear notion of date,
even to people that are new to the project.

>>>>

The traditional academic system has limited ways of recognizing contributions.
Until systems have been expanded to improve this,
it is important to publish your lessons using a mechanism that provides recognition to the contributors.
Currently an effective way to do this is
to publish lessons with a DOI supplied by providers such as Zenodo\footnote{https://zenodo.org/} or DataCite\footnote{https://zenodo.org/}.
Contributors can be listed as authors
and the maintainers of the lesson as editors
to provide differentiated recognition of their contributions.

A lesson release is a good opportunity to bring the material into a stable shape
by fixing outstanding issues and merging contribution.
The complete name and possible identifier like ORCID should also be gathered for every contributor.
Version control helps a lot in continuously maintaining a list of contributors
but also in remembering which version is used for release
(e.g., using branches or tags).
A lesson release is a permanent snapshot of the lesson
and it is recommended to use a consistent naming scheme from the beginning.
A convenient naming scheme is to use the full year and month of the release,
like ``2017.05'',
as it conveys a clear notion of date,
even to people that are new to the project.
